---
title: "Skincare Recommender Report"
author: "Natisya"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Beauty and Wellness: Skin Care Recommender Engine

```{r}
data <- read.csv("skincare_products.csv")
```

## Data Cleaning
```{r}
str(data)     # Check the structure of the dataset
summary(data) # Calculate summary statistics of the dataset
```

```{r}
# Identify missing values
missing_values <- is.na(data)

# Count the number of missing values per variable
colSums(missing_values)
```

```{r}
#focus on face skincare, remove product types related with body care.
# Remove rows where 'product_type' is 'Bath Salts'
data <- data[data$product_type != "Bath Salts", ]

# Remove rows where 'product_type' is 'Bath Oil'
data <- data[data$product_type != "Bath Oil", ]

# Remove rows where 'product_type' is 'Body Wash'
data <- data[data$product_type != "Body Wash", ]
```

```{r}
# Convert 'price' column to float
data$price <- as.numeric(gsub("[^0-9.]", "", data$price))
```

```{r}
# Set the CRAN mirror
options(repos = c(CRAN = "https://cran.rstudio.com"))

# Install the dplyr package
if (!require(dplyr)) {
  install.packages("dplyr")
}

# Load the dplyr package
library(dplyr)
```

```{r}
# Print the shape of the dataframe
cat("Number of rows:", nrow(data), "\n")
cat("Number of columns:", ncol(data), "\n")

# Create a dataframe with the counts of each product type
Prod_Type <- data.frame(table(data$product_type))
colnames(Prod_Type) <- c("product_type", "count")

# Print the dataframe
print(Prod_Type)

# Group by 'product_type' and calculate the mean price
PricexProd <- data %>%
  group_by(product_type) %>%
  summarize(mean_price = mean(price)) %>%
  arrange(desc(mean_price))

# Print the result
print(PricexProd)
```

There are 946 items remaining after 192 products were removed, with the majority being masks, moisturisers, and cleansers. Additionally, peelings, serums, and eye care are generally more expensive compared to other products, possibly having more of the components that give its formula its greatness.

```{r}
glimpse(data)
```

```{r}
# CREATING NEW VARIABLE "brand"
# Define the specific brand names to consider
specific_brands <- c("Alchimie Forever","Aromatherapy Associates","Balance Me","Bloom & Blossom","Bobbi Brown","Bondi Sands","Bubble T","Burt's Bees",
                     "By Terry","Comfort Zone","Dear, Klairs", "Dr Dennis Gross","Dr. Hauschka","Dr. Brandt","Dr. Hauschka","Dr. PAWPAW","Egyptian Magic",
                     "Elizabeth Arden","Emma Hardie","Erno Laszlo","Estee Lauder","Eve Lom","Face by Skinny Tan","Fade Out","First Aid Beauty",
                     "Frank Body","Goldfaden MD","Holika Holika","Indeed Labs","Instant Effects","Institut Esthederm","James Read","Jo Malone","L.A BRUKET",
                     "La Roche-Posay","Lancer Skincare","Laura Mercier","Little Butterfly","Liz Earle","L'Oreal Paris","Love Boo","Lumene Nordic",
                     "Mama Mio","Manuka Doctor","Molton Brown","Natura Bisse","Neal's Yard","Oh K!","Perricone MD","Pestle & Mortar",
                     "Peter Thomas","Piz Buin","Radical Skincare","Recipe for Men","Revolution Skincare","Salcura Antiac","Sanctuary Spa",
                     "Sarah Chapman","Sea Magik","Skin Doctors","Sol de Janeiro","Spa Magik Organiks","Talika Skintelligence","The Chemistry",
                     "The INKEY","The Ordinary","The Organic Pharmacy","The Ritual","Too Faced","yes to")

# Create a new variable 'brand' by extracting data from 'product_name' based on specific criteria
data$brand <- ""
for (brand in specific_brands) {
  data$brand <- ifelse(grepl(brand, data$product_name), brand, data$brand)
}
data$brand[data$brand == ""] <- gsub("\\s.*", "", data$product_name[data$brand == ""])
```

## Exploratory Data Analysis

```{r}
library(tidyr)
library(ggplot2)
```

```{r}
# Calculate the count of each brand
brand_counts <- data %>%
  count(brand) %>%
  arrange(desc(n))

# Average price by brand
avg_price_by_brand <- data %>%
  group_by(brand) %>%
  summarise(avg_price = mean(price, na.rm = TRUE)) %>%
  arrange(desc(avg_price))

# Display top 10 brands
top_10_brands <- head(avg_price_by_brand, 10)

# Create a vertical bar chart of the average prices of the top 10 brands
ggplot(top_10_brands, aes(x = reorder(brand, -avg_price), y = avg_price)) +
  geom_bar(stat = "identity", fill = "lightblue") +
  labs(title = "Top 10 Brands by Average Price", x = "Brand", y = "Average Price") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
# Create the chart: Distribution of product type
chart1 <- ggplot(data, aes(x = product_type)) +
  geom_bar(fill = "lightblue", color = "black") +
  labs(title = "Distribution of Product Types", x = "Product Type", y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
print(chart1)
```

### Dealing with Outliers
```{r}
# Create the boxplot before removing outliers
boxplot_before <- ggplot(data, aes(y = price)) +
  geom_boxplot() +
  labs(title = "Boxplot of Price (Before Removing Outliers)", y = "Price") +
  theme_minimal()
print(boxplot_before)

# Calculate the lower and upper bounds for outliers using the IQR method
q1 <- quantile(data$price, 0.25)
q3 <- quantile(data$price, 0.75)
iqr <- q3 - q1
lower_bound <- q1 - 1.5 * iqr
upper_bound <- q3 + 1.5 * iqr

# Remove outliers
data_filtered <- subset(data, price >= lower_bound & price <= upper_bound)

# Create the boxplot after removing outliers
boxplot_after <- ggplot(data_filtered, aes(y = price)) +
  geom_boxplot() +
  labs(title = "Boxplot of Price (After Removing Outliers)", y = "Price") +
  theme_minimal()
print(boxplot_after)
```

### Analyze Relationship between Variables
```{r}
# Create the contingency table
cont_table <- table(data$brand, data$product_name)

# Perform chi-square test of independence
chi_test <- chisq.test(cont_table)

# Print the test results
print(chi_test)
```

*   The analysis results indicate that there is no meaningful relationship between the variables "Brand" and "Product Name" in the dataset. The p-value obtained from the statistical test is 0.3814, which is higher than the standard significance level of 0.05. Therefore, we do not have enough evidence to disprove the null hypothesis of independence between "Brand" and "Product Name".

*   Based on these findings, we can infer that the brand name distribution across various product names, or vice versa, does not vary noticeably. There does not seem to be a substantial correlation between the brand information derived from the product names and the particular product names themselves.

```{r}
# Create the contingency table
cont_table <- table(data$clean_ingreds, data$product_type)

# Perform chi-square test of independence
chi_test <- chisq.test(cont_table)

# Print the test results
print(chi_test)
```
*   The "Clean Ingreds" and "Product Type" variables in the dataset show a significant correlation with a p-value of 0.0004713, which is below the standard significance level of 0.05.
*   According to the chi-square test, the distribution of "Clean Ingreds" categories changes significantly across the "Product Type" categories, or vice versa. In other words, there is proof that the type of product and the ingredients are associated.


```{r}
install.packages("wordcloud")
install.packages("tm")
library(wordcloud)
library(tm)
```

```{r}
# Word cloud of clean ingredients
clean_ingreds <- unlist(strsplit(data$clean_ingreds, ","))
wordcloud(clean_ingreds, max.words = 50, random.order = FALSE)
```

